Model exploration

### 2015-03-06 documentation/model_exploration.Rmd
model exploration edits

The paper departs from a general perception of grazing systems as non-equilibrium systems that are subject to 'dynamic regimes' or 'alternative stable states'.
This means, they can shift their attractor between a vegetated state and a degraded state, if they experience a sufficient perturbation.
The question is how resilience thinking in managed rangelands can be improved [@folke06; @walker04; @walker12; @folke10]. How can the ecosystem be put in a state that is far from the tipping point or the critical thresholds [@may75; @westoby89; @walker81]?

It aims at an integration of spatial grazing mortality into a graphical population-dynamics framework as developed by @noy-meir75 and extended by @vandekoppel97 and @rietkerk97.
The model is of conceptual character and identifies how certain management practices or characteristics of vegetation affect the thresholds of catastrophic shifts. This kind of model can be used to inform state-and-transition models that are of high relevance in decisionmaking in the management of rangelands [@westoby89; @briske05; @bestelmeyer03; @briske08].

@@

The model is neutral in terms of species and assumes only one relevant type of vegetation and one population of grazer. Noy-meir notes that the model can apply also if there is one plant species that dominates the ecological dynamics of the entire system. [@noy-meir75]
We stick to this approach of neglecting species-specific differences.

>>>>

The paper departs from a general perception of grazing systems as non-equilibrium systems that are subject to 'dynamic regimes' or 'alternative stable states'.
This means, they can shift their attractor between a vegetated state and a degraded state, if they experience a sufficient perturbation.
The question is how resilience thinking in managed rangelands in arid and semi-arid ecosystems can be improved [@folke06; @walker04; @walker12; @folke10]. How can the ecosystem be put in a state that is far from the tipping point or the critical thresholds [@may75; @westoby89; @walker81]?

It aims at an integration of local feedback mechanisms in drylands into a graphical population-dynamics framework as developed by @noy-meir75 and extended by @vandekoppel97 and @rietkerk97.
The model identifies how certain mechanisms of vegetation affect the thresholds of catastrophic shifts. This kind of model can be used to inform state-and-transition models that are of high relevance in decisionmaking in the management of rangelands [@westoby89; @briske05; @bestelmeyer03; @briske08].

@@

The model is neutral in terms of species and assumes only one relevant type of vegetation and one population of grazer. Noy-meir notes that the model can apply also if there is one plant species that dominates the ecological dynamics of the entire system [@noy-meir75].
We stick to this approach of neglecting species-specific differences.
